### 2020-11-20 ch01_introduction/introduction.tex
Added further text and figures to ch.2

Parts of this thesis are published in multiple scientific publications (two as
first author six as co-author). If applicable, this is clearly stated at the
beginning of each chapter. \Cref{ch:02:scientific_background} introduces the
scientific background for this thesis. This includes basic principles of Earth
System Modeling, sources of uncertainty in future projections of the climate,
relevant definitions and state-of-the-art methods used to evaluate \ac{ESM}
simulations and reduce associated uncertainties. \Cref{ch:03:esmvaltool} gives
an overview over the contributions made to the \ac{ESMValTool}, an open-source
software for the analysis of \acp{ESM}. These contributions helped improving
the routine evaluation of \acp{ESM} which is useful for the whole scientific
community and lead to co-authorship in four peer-reviewed studies
\autocite{Righi2020, Eyring2020, Lauer2020, Weigel2020}.
\Cref{ch:04:assessment_climate_metrics} covers the assessment of
policy-relevant climate metrics like the \ac{EqCS} and the \ac{TCR} in the
latest generation of \acp{ESM}. This work is already published in two
scientific publications \autocite{Bock2020, Meehl2020}. Since the \ac{EqCS} and
\ac{TCR} are considerably higher in this new climate model generation,
\cref{ch:05:paper_ecs} describes the assessment of emergent constraints (a
technique to reduce uncertainties in climate model projections, see
\vref{sec:02:techniques}) on the \ac{EqCS} for these \acp{ESM}. The contents of
this chapter are published in \emph{Earth System Dynamics}
\autocite{Schlund2020a}. \Cref{ch:06:paper_gpp} focuses on a new method to
reduce climate model uncertainties based on \ac{ML}. As an example, the method
is applied to the photosynthesis rate at the end of the \nth{21} century, which
is already published in the \emph{Journal of Geophysical Research:
Biogeosciences} \autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook}
provides a summary of the results of this thesis and gives an outlook of
possible future works.

>>>>

Parts of this thesis are published in multiple peer-reviewed publications (two
first-author studies and six co-author studies). If applicable, this is clearly
stated at the beginning of each chapter. \Cref{ch:02:scientific_background}
introduces the scientific background for this thesis. This includes relevant
literature that is used as a baseline for this thesis. \Cref{ch:03:esmvaltool}
gives an overview over the contributions made to the \ac{ESMValTool}, an
open-source software for the analysis of \acp{ESM}. These contributions helped
improving the routine evaluation of \acp{ESM} which is useful for the whole
scientific community and lead to co-authorship in four peer-reviewed studies
\autocite{Righi2020, Eyring2020, Lauer2020, Weigel2020}.
\Cref{ch:04:assessment_climate_metrics} covers the assessment of
policy-relevant climate metrics like the \ac{ECS} and the \ac{TCR} in the
latest generation of \acp{ESM}. This work is already published in two
scientific publications \autocite{Bock2020, Meehl2020}. Since the \ac{ECS} and
\ac{TCR} are considerably higher in this new climate model generation,
\cref{ch:05:paper_ecs} describes the assessment of emergent constraints (a
technique to reduce uncertainties in climate model projections, see
\vref{sec:02:techniques}) on the \ac{ECS} for these \acp{ESM}. The contents of
this chapter are published in \emph{Earth System Dynamics}
\autocite{Schlund2020a}. \Cref{ch:06:paper_gpp} focuses on a new method to
reduce climate model uncertainties based on \ac{ML}. As an example, the method
is applied to the photosynthesis rate at the end of the \nth{21} century, which
is already published in the \emph{Journal of Geophysical Research:
  Biogeosciences} \autocite{Schlund2020}. Finally, \cref{ch:07:summary_outlook}
provides a summary of the results of this thesis and gives an outlook of
possible future works.

### 2020-11-20 ch02_scientific_background/scientific_background.tex
Added further text and figures to ch.2

\section{Earth System Models: Simulations and Analysis}
\label{sec:02:esms}

An \ac{ESM} is really cool! Yes, \acp{ESM}!!

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidth{}]{
    ch02_scientific_background/figs/esms_historical_evolution.pdf}
  \caption{Historical evolution of coupled climate models over the last 45
  years. In early days, these models were \acfp{AOGCM} and only included three
  components: the atmosphere, the land surface and the ocean. Over the time,
  the individual components grew in complexity and included a wider range of
  processes (illustrated by the growing cylinders). Eventually, more and more
  components (aerosols, carbon cycle, \etc{}) were added to the coupled system,
  forming the modern \acfp{ESM}. Taken from \textcite{Cubasch2013}.}
  \label{fig:02:esms_historical_evolution}
\end{figure}

TBA.

@@

>>>>

This chapter introduces the scientific background necessary for the work
presented in this thesis. After a brief introduction to climate model
simulations and associated uncertainties, we present state-of-the art
techniques used to evaluate climate model simulations and reduce uncertainties
in projections of the future climate. These methods form the basis for the new
techniques developed in this thesis.

\section{\aclp{ESM}: Simulations and Analysis}
\label{sec:02:esms}

In contrast to other fields of science, researching the future evolution of the
Earth's climate cannot be purely done by performing experiments in a
laboratory. Due to the immense complexity of the Earth system (including
physical, biological and chemical processes on various temporal and spatial
scales), we do not have access to a mini version of the Earth that we can
expose to varying external conditions and analyze its response to it
\autocite{Flato2011}. While observing the current state of the Earth System is
(relatively) straightforward, gaining evidence about the future climate by only
considering present-day observations is rather difficult. A possible way out is
given by numerical climate models, which offer the possibility to simulate the
Earth's climate on a computer. The first numerical climate models came up in
the 1960s and were based on weather prediction models \autocite{Flato2011}.
Early models from the 1970s simulated only the physical components of the
climate system: atmosphere, land surface, ocean and sea ice (see
\cref{fig:02:esms_historical_evolution}). The main aim of these so-called
\acp{AOGCM} \autocite{Flato2013} is to numerically solve the differential
equations that describe the exchange of energy and matter between these
physical components.

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidth{}]{
    ch02_scientific_background/figs/esms_historical_evolution.pdf}
  \caption{Historical evolution of coupled climate models over the last 45
    years. In early days, these models were so-called \acfp{AOGCM} and only
    included three components: the atmosphere, the land surface and the ocean.
    Over the time, the individual components grew in complexity and included a
    wider range of processes (illustrated by the growing cylinders). Eventually,
    more and more components (aerosols, carbon cycle, \etc{}) were added to the
    coupled system, forming the modern \acfp{ESM}. Taken from
    \textcite{Cubasch2013}.}
  \label{fig:02:esms_historical_evolution}
\end{figure}

Over the course of the years, climate models became more and more complex by
including a wider range of processes within the components, but also by
introducing new components to the coupled system. Examples of these are
aerosols, the carbon cycle, a dynamic vegetation, atmospheric chemistry and
land ice (see \cref{fig:02:esms_historical_evolution}). \acp{AOGCM} coupled to
these additional components are called \acfp{ESM}, which are the current
state-of-the-art models that allow the most sophisticated simulations of the
Earth's climate. In contrast to \acp{AOGCM}, \acp{ESM} enable the simulation of
biological and chemical processes in addition to the dynamics of the physical
components of the Earth system. Especially in the context of anthropogenic
climate change, these additional processes are of uttermost importance for
realistic climate model simulations, since the anthropogenic interference with
the Earth system directly influences the various biogeochemical cycles of the
Earth. For example, the emission of the most prominent \ac{GHG}, \ac{CO2},
immediately impacts the global carbon cycle by introducing an additional carbon
source to the cycle (for details see \cref{sec:02:carbon_cycle}). Due to the
global carbon cycle, only about \pct{50} of the emitted \ac{CO2} remains in the
atmosphere, where it can act as \ac{GHG} by introducing an additional radiative
forcing to the Earth System, which eventually leads to increasing surface
temperatures. Thus, this uptake of \ac{CO2} by the global carbon cycle slows
down global warming. Further examples include land use changes like the
deforestation of tropical rainforests, which also directly influences several
biogeochemical cycles (\eg{} carbon cycle, nitrogen cycle, phosphorus cycle,
\etc{}) by altering respective sinks and sources.

@@

\section{The global Carbon Cycle}
\label{sec:02:carbon_cycle}
